---
title: "Calibration Report"
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
check.packages <- function(package){
  new.package <- package[!(package %in% installed.packages()[, "Package"])]
  if (length(new.package)) 
    install.packages(new.package, dependencies = TRUE)
  sapply(package, require, character.only = TRUE)
}

suppressWarnings(suppressPackageStartupMessages(check.packages(c("tidyverse", "readxl", "investr", "broom", "here", "kableExtra"))))

knitr::opts_chunk$set(echo = FALSE, messages = FALSE)

source("readWatersQQQReport.R")
source("calibration.R")

#source("C:/Users/Orbitrap-Processing/Documents/R Scripts/Calibration-Reports/Metabolism Study/metabolism_study.R")

```
# Experiment Summary
```{r summary}
sSummary <- input %>%
  filter(Cmp == the.Compounds) %>%
  group_by(Sample.Type) %>%
  summarize(count = n(),
            mean_Reponse = mean(Raw.Response),
            sd_Response = sd(Raw.Response),
            mean_ISTDReponse = mean(ISTD.Response),
            sd_ISTDResponse = sd(ISTD.Response))
```

Experimental summary report for `r the.Compounds` from batch `r unique(input$Batch)`. 

A total of `r sum(sSummary$count)` samples were run in this batch, containing `r sSummary[[which(sSummary$Sample.Type == "Blank"), 'count']]` blanks, and `r sSummary[[which(sSummary$Sample.Type == "Sample"), 'count']]` samples.

## Raw Values Summary {.tabset}

### Blanks
```{r blank_summary, fig.align = "center", fig.show = "hold"}

bSummary <- input %>% filter(Cmp == the.Compounds, Sample.Type == "Blank") %>%
  arrange(Sample.ID) %>% 
  rename(`Run Order` = Sample.ID) %>%
  select(Sample.Name, Sample.Desc, `Run Order`, Raw.Response, ISTD.Response)

bSummary

bSummary_plot <- bSummary %>% gather(contains("Response"), key = "Response", value = "Signal")

ggplot(bSummary_plot) +
  theme_bw()+
  geom_point(aes(x = "X", y = Signal, color = Response)) + 
  scale_x_discrete(labels = "") +
  facet_wrap(~Sample.Desc, scales = "free_y") +
  labs( x = "")


ggplot(bSummary_plot) +
  theme_bw()+
  geom_point(aes(x = `Run Order`, y = Signal, color = Response)) +
  facet_wrap(~Sample.Desc, scales = "free_y")


```

### Samples
```{r sampleraws_summary}

srSummary <- input %>% filter(Cmp == the.Compounds, Sample.Type == "Sample") %>%
  arrange(Sample.ID) %>% 
  rename(`Run Order` = Sample.ID) %>%
  select(Sample.Name, Sample.Desc, `Run Order`, Raw.Response, ISTD.Response)

srSummary

srSummary_plot <- srSummary %>% gather(contains("Response"), key = "Response", value = "Signal")

ggplot(srSummary_plot) +
  theme_bw()+
  geom_point(aes(x = "X", y = Signal, color = Response)) + 
  scale_x_discrete(labels = "") +
  labs( x = "")


ggplot(srSummary_plot) +
  theme_bw()+
  geom_point(aes(x = `Run Order`, y = Signal, color = Response))


```




## Calibration Summary {.tabset}

### Calibration
``` {r calibration_summary}

cSummary <- input %>% filter(Cmp == the.Compounds, Sample.Type == "Standard") %>%
  arrange(Sample.ID) %>% 
  mutate(Area.Ratio = Raw.Response/ISTD.Response) %>%
  rename(`Run Order` = Sample.ID,
         Std.Conc = Exp.Amt)

prettyPrint_calibration(calibrations, the.Compounds)

cSummary <- prettySummary_calibration(calibrations, the.Compounds)  %>% 
  left_join(cSummary) %>%
  select(Sample.Name, Sample.Desc, `Run Order`, Raw.Response, ISTD.Response, Std.Conc, estimate, lower, upper, dev) 

cSummary_table <- cSummary %>%
  mutate(dev = cell_spec(dev, color = ifelse(abs(dev) > 20, "red", "black"))) %>%
  rename(`% Dev` = dev,
         Estimated.Conc = estimate,
         lower_est = lower,
         upper_est = upper)

cSummary_table

```

### QC Samples
``` {r QC_summary}

qSummary <- input %>% filter(Cmp == the.Compounds, Sample.Type == "QC") %>%
  arrange(Sample.ID) %>% 
  mutate(Area.Ratio = Raw.Response/ISTD.Response) %>%
  rename(`Run Order` = Sample.ID,
         Std.Conc = Exp.Amt)

if (dim(qSummary)[1] != 0) {

getSamplePredictions(qSummary)

cSummary <- prettySummary_calibration(calibrations, the.Compounds)  %>% 
  left_join(cSummary) %>%
  select(Sample.Name, Sample.Desc, `Run Order`, Raw.Response, ISTD.Response, Std.Conc, estimate, lower, upper, dev) 

 cSummary_table <- cSummary %>%
  #mutate(dev = cell_spec(dev, "latex", color = ifelse(abs(dev) > 20, "red", "black"))) %>%
  rename(`% Dev` = dev,
         Estimated.Conc = estimate,
         lower_est = lower,
         upper_est = upper)

cSummary_table
}

```


## Sample Summary 
``` {r sample_summary}
preds <- input %>%
  filter(Cmp == the.Compounds) %>%
  group_by(Batch) %>%
  do(getSamplePredictions(.)) %>%
  inner_join(input) %>%
  ungroup() %>%
  filter(!Sample.Type %in% c("Blank","Standard")) %>%
  select(Sample.Name, Sample.Desc, Sample.ID, Raw.Response, ISTD.Response, estimate, lower, upper) %>%
  rename(`Estimated.Conc` = estimate,
         lower_est = lower,
         upper_est = upper,
         `Run Order` = Sample.ID)

preds

preds_plot <- preds %>% arrange(Sample.Desc)

ggplot(preds_plot) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  scale_x_discrete(labels = abbreviate) +
  geom_point(aes(x = Sample.Desc, y = Estimated.Conc)) +
  geom_errorbar(aes(x = Sample.Desc, ymin = lower_est, ymax = upper_est), width = 0.2)
```

